### 2015-07-07 Irregular-occ/Irregular-occ.tex
começado a correção do qualify
.

%The irregular satellites of the giant planets are smaller than the regular moons, having more eccentric, inclined, distant and, in most cases, retrograde orbits. Due to their orbital configurations, it is largely accepted that these objects were captured in the early solar system \citep{Sheppard2003}.

@@

%There is a number of capture mechanisms of objects by giant planets proposed in the literature. There is the Gas Drag in the primordial circumplanetary nebulae \citep{Sheppard2006} where the object would be affected by the gas drag and its velocity slowed down until it be captured by the planet. Another mechanism is called pull-down capture \citep{Sheppard2006}, where the mass of the planet would increase while the object was temporarily captured.

%A mechanism based in the Nice model \citep{Morbidelli2005, Tsiganis2005, Gomes2005} was proposed by \citealp{Nesvorny2007} and, in the specific case of Jupiter with the modern Nice model, by \citealp{Nesvorny2014}. During the early solar system instability, encounters between the outer planets occurred. These planetary encounters could exchange energy and angular momentum between planets and the objects nearby making it possible for the capture of irregular bodies by the giant planets. In this scenario, the survival rate of prior-LHB (Late Heavy Bombardment) satellites is very small.

%Another important mechanism is the capture through collisional interactions \citep{Sheppard2006}. A collision between two small bodies in the Hill's sphere of the planet could generate fragmented objects and the dissipated energy could be such that some of these objects could be captured.

%Some of these objects are in dynamical groups with similar orbital elements, called families, similar to families found in the Main Asteroid Belt. These families may have been created by a parent body disrupted by collisions with comets or other satellites \citep{Nesvorny2004}. Collisions with comets are more likely to have occurred during the Late Heavy Bombardment (LHB) \citep{Gomes2005}.

%\citealp{Nesvorny2003} studied the collision rates between irregular satellites and concluded that some satellites could have been removed by collision with a bigger satellite. The rate collision between satellites of the Himalia Group (Himalia, Elara, Lysithea and Leda, mainly), for instance, was found to be more than one during the solar system age suggesting that their current structure was originated by satellite-satellite collision.

%For Phoebe, ejected material from its surface caused by impacts could evolve due to Poynting-Robertson drag and collide with Iapetus causing the large variation in albedo observed on it \citep{Nesvorny2003}. Indeed, Cassini was able to detected in Phoebe an absorption feature at 2.42 $\mu m$ (probably CN combinations) that was also detected in the dark side of Iapetus \citep{Clark2005}.

@@

\section{Conclusions} \label{Sec: conclusions}

>>>>

Irregular satellites, also known as outer satellites, of the giant planets are objects orbiting the planets from a distant, eccentric and highly inclined orbit, most of them are retrograde. Because of these peculiar orbits, it is largely accepted that these objects were captured by their planets in the early solar system \citep{Sheppard2005}.

There is a number of capture mechanisms of objects by giant planets proposed in the literature. There is the Gas Drag in the primordial circumplanetary nebulae \citep{Sheppard2005} where the object would be affected by the gas drag and its velocity slowed down until it be captured by the planet. Another mechanism is called pull-down capture \citep{Sheppard2005}, where the mass of the planet would increase while the object was temporarily captured.

A mechanism based in the Nice model \citep{Morbidelli2005, Tsiganis2005, Gomes2005} was proposed by \cite{Nesvorny2007} and, in the specific case of Jupiter with the modern Nice model, by \citealp{Nesvorny2014}. During the early solar system instability, encounters between the outer planets occurred. These planetary encounters could exchange energy and angular momentum between planets and the objects nearby making it possible for the capture of irregular bodies by the giant planets. In this scenario, the survival rate of prior-LHB (Late Heavy Bombardment) satellites is very small.

Another important mechanism is the capture through collisional interactions \citep{Sheppard2005}. A collision between two small bodies in the Hill's sphere of the planet could generate fragmented objects and the dissipated energy could be such that some of these objects could be captured.

Some of these objects are in dynamical groups with similar orbital elements, called families, similar to families found in the Main Asteroid Belt. These families may have been created by a parent body disrupted by collisions with comets or other satellites \citep{Nesvorny2004}. Collisions with comets are more likely to have occurred during the Late Heavy Bombardment (LHB) \citep{Gomes2005}.

\cite{Nesvorny2003} studied the collision rates between irregular satellites and concluded that some satellites could have been removed by collision with a bigger satellite. The rate collision between satellites of the Himalia Group (Himalia, Elara, Lysithea and Leda, mainly), for instance, was found to be more than one during the solar system age suggesting that their current structure was originated by satellite-satellite collision.

For Phoebe, ejected material from its surface caused by impacts could evolve due to Poynting-Robertson drag and collide with Iapetus causing the large variation in albedo observed on it \citep{Nesvorny2003}. Indeed, Cassini was able to detected in Phoebe an absorption feature at 2.42 $\mu m$ (probably CN combinations) that was also detected in the dark side of Iapetus \citep{Clark2005}.

The region of origin of these object is not well known, \cite{Grav2003} and \cite{Grav2007} showed that the irregular satellites from the giant planest have their colors and spectral slopes similar to C-, D- and P-type asteroids, Centaurs and trans-neptunian objects (TNOs) suggesting that they have been originated from different locations in the early solar system.

In this work, we study these objects as possible representatives of the small TNOs population. TNOs are objects that due to their distance may be highly preserved having their properties similar to those they had when they were formed then providing history and evolution of the outer solar system \citep{Camargo2013}. Due to their distance, the smaller objects from this region are more difficult to observe and study.

In the intent to obtain their physical parameters (size, shape, albedo, density, etc) and help identify their origin locations, we will make use of the stellar occultation technique. This technique is the best one to obtain the physical parameters of the solar system objects from ground-based observations providing more accurate results than other techniques \citep{Sicardy2011, Ortiz2012, Braga-Ribas2014}.

Since their sizes are very small (see table \ref{}), predict the exact location and instant where the shadow will cross the Earth demands a good precision. For instance, the bigger irregular satellite of Jupiter has an estimated size of 150 km \citep{Porco2003}, which is equivalent to an apparent size of 40 mas, must have an error smaller than its size for being observable. For the other objects, smaller or farther than Himalia, the situation is more difficult.

As pointed out by \cite{GomesJunior2015}, the ephemeris of the irregular satellites have errors that may reach 200 mas for some satellites. For an object at the distance of Jupiter, this represents an error bigger than 700 km in the shadow path.

We present in this paper the stellar occultation predictions for the 8 major irregular satellites of Jupiter (Himalia, Elara, Pasiphae, Lysithea, Carme, Ananke and Sinope), Phoebe from Saturn and Nereid from Neptune. In the section \ref{Sec: Rationale} we explore the scientific rationale for study the irregular satellites. In section \ref{Sec: Offset} we show the correction made to the ephemeris for better predict stellar occultations. In section \ref{Sec: predictions}, we present the predictions of the stellar occultations by irregular satellites. Some test realized to confirm the predictions are presented in section \ref{Sec: testes} and the conclusion is given in section \ref{Sec: conclusions}.

\section{Scientific Rationale} \label{Sec: Rationale}

@@

@@

\section{Correction of the ephemeris} \label{Sec: Offset}

\section{Prediction of occultations} \label{Sec: predictions}

%The prediction of the occultations was made by crossing the stellar coordinates and proper motions of the UCAC4 catalogue \citep{Zacharias2013} with the corrected JPL ephemeris as presented in the section \ref{Sec: Offset}.

\section{Occultation tests} \label{Sec: testes}

\section{Conclusion} \label{Sec: conclusions}
